Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-19 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling
\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believe quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it could be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
theorem exclude any non-contextuality hidden variable model for any
Hilbert space of dimension $d\ge3$, Meyer claimed that finite-precision
measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751}.
This claim was countered in the same year by Havlicek et al.~\cite{HKSS1999}
and Mermin~\cite{Mermin1999} and the debate continues to be an active
topic of research \cite{Kent1999,SimonBruknerZeilinger2001,Cabello2002,Appleby2002,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
In our investigation~\cite{THOS2017}, we employ an interval-valued
framework to establish bounds on the validity of the Kochen-Specker
theorem in realistic experimental environments. In another word, when
measurements are precise enough, quantum-mechanical contextuality
continues to hold, the Kochen-Specker theorem maintains, and our results
provide additional trust of the randomness of quantum theory.

>>>>

\maketitle
Randomness is exploited in cryptography, algorithmic complexity, and
gambling. While quantum physics is associated to randomness, it could
be causally deterministic if it were simulated by a classical non-contextual
hidden-variable model. The Kochen-Specker theorem excludes such models.
However, its main tenet has been questioned because finite-precision
measurements, i.e. errors in preparation or observation, might invalidate
its spirit. Our work, by introducing an interval-valued probabilistic
framework, establishes bounds on the validity of the Kochen-Specker
theorem in realistic, i.e., error-non-free, experimental environments.
The conclusion is that a quantum theory of measurement that includes
errors in the probability outcomes can still provide a valid test
of contextuality, as long as the error is bounded by a finite amount.
